Manuscript Figures for Genome Biology

### 2019-04-02 manuscript_figures/manuscript_figures_supp.Rmd

---
title: "Manuscript Figures for Genome Biology"
author: "Rafalab"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

>>>>

---
title: "Manuscript Figures for Genome Biology"
author: "Rafalab"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

# Figure SR1 (added in response to reviewer comments)

This is a figure that combines Figure 2A and 3A into one plot (mean FDR vs mean TPR), with open or
closed circles representing whether or not the nominal error rate is controlled (on average) at three 
points (0.01, 0.05, 0.10).

```{r}
# methods to include in all figures ( exclude bonferroni and fdrreg-e)
alpha <- alpha.thresh
methodset <- c("bh", "ihw", paste0("ihw-a0", 1:9), "ihw-a10", 
               "qvalue", "bl", "bl-df03", "lfdr",
               "fdrreg-t", "ashq", "adapt-glm")
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast-", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)] 
de5 <- readRDS(file=resfile)
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01)) %>% 
  filter(blabel %in% methodset)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05", "bonf", "fdrreg-e")
r1.1a <- plotsim_average(res5d, met=c("FDR", "TPR"), filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ggtitle("FDR vs TPR") +
      scale_x_continuous("FDR", breaks=seq(0, 1, by=0.01))

res5d.sum <- res5d %>% 
  group_by(blabel, performanceMetric, alpha, param.alpha, key) %>%
  summarize(n = sum(!is.na(value)),
            se = sd(value, na.rm = TRUE) / sqrt(n),
            value = mean(value, na.rm = TRUE)) %>%
  filter(round(alpha,2) %in% c(0.01, 0.05, 0.1),
         performanceMetric %in% c("FDR", "TPR"),
         !blabel %in% excludeSet,
         is.na(param.alpha) | (param.alpha == alpha))

tsba_m <- NULL 
met = c("FDR", "TPR")
for (m in seq_along(met)){
     tmp <- res5d.sum %>% 
     filter(performanceMetric == met[m]) %>%
     dplyr::mutate(Method = gsub("-df03", "", blabel)) 
     if (m > 1){
      tsba_m <- left_join(tsba_m, tmp, 
                          by = c("Method", "alpha", "n", 
                                 "param.alpha", "blabel"))
  }else{
      tsba_m <- tmp
  }
}
res5d.sum <- tsba_m
res5d.sum <- res5d.sum %>%
  mutate(control = value.x < alpha)

# add color palette
res5d.sum$Method[grepl("^ihw-", res5d.sum$Method)] <- "ihw"
res5d.sum <- dplyr::left_join(res5d.sum, candycols, by="Method") %>%
  mutate(col2 = ifelse(control, col, "white"))

r1.1a <- r1.1a +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  scale_shape_manual(values = c(1, 19)) + 
  ggtitle("In silico experiments") +
  scale_x_continuous(breaks=seq(0, 1, by=0.02))
```

Next we'll do the same for 2B and 3B (polyester).

```{r}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("polyester-", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)] 
de5 <- readRDS(file=resfile)
res5dp <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01)) %>% 
  filter(blabel %in% methodset)
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05", "bonf", "fdrreg-e")
r1.1b <- plotsim_average(res5dp, met=c("FDR", "TPR"), filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ggtitle("FDR vs TPR") +
      scale_x_continuous("FDR", breaks=seq(0, 1, by=0.01))

res5d.sum <- res5dp %>% 
  group_by(blabel, performanceMetric, alpha, param.alpha, key) %>%
  summarize(n = sum(!is.na(value)),
            se = sd(value, na.rm = TRUE) / sqrt(n),
            value = mean(value, na.rm = TRUE)) %>%
  filter(round(alpha,2) %in% c(0.01, 0.05, 0.1),
         performanceMetric %in% c("FDR", "TPR"),
         !blabel %in% excludeSet,
         is.na(param.alpha) | (param.alpha == alpha))

tsba_m <- NULL 
met = c("FDR", "TPR")
for (m in seq_along(met)){
     tmp <- res5d.sum %>% 
     filter(performanceMetric == met[m]) %>%
     dplyr::mutate(Method = gsub("-df03", "", blabel)) 
     if (m > 1){
      tsba_m <- left_join(tsba_m, tmp, 
                          by = c("Method", "alpha", "n", 
                                 "param.alpha", "blabel"))
  }else{
      tsba_m <- tmp
  }
}
res5d.sum <- tsba_m
res5d.sum <- res5d.sum %>%
  mutate(control = value.x < alpha)

# add color palette
res5d.sum$Method[grepl("^ihw-", res5d.sum$Method)] <- "ihw"
res5d.sum <- dplyr::left_join(res5d.sum, candycols, by="Method") %>%
  mutate(col2 = ifelse(control, col, "white"))

r1.1b <- r1.1b +
  geom_point(data=res5d.sum, aes(x = value.x, y = value.y, 
             shape = control), size = 3.5) +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 19, size = 2.5, color = "white") +
  geom_point(data=res5d.sum %>% filter(!control), aes(x = value.x, y = value.y), 
             shape = 1, size = 3.5) +
  scale_shape_manual(values = c(1, 19)) +
  ggtitle("Polyester") +
  scale_x_continuous(breaks=seq(0, 1, by=0.02))
```

Put them together and save.

```{r}
r1.1 <- plot_grid(r1.1a, r1.1b, rel_widths = c(1,1.05))
r1.1 <- plot_grid(r1.1, leg, rel_widths = c(1, .2)) 
r1.1
ggsave(file.path(outdir, "Figure_SR1.pdf"), width = 8, height = 3)
```
